---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mappers

<!-- badges: start -->
[![R build status](https://github.com/jameelalsalam/mapping/workflows/R-CMD-check/badge.svg)](https://github.com/jameelalsalam/mapping/actions)
<!-- badges: end -->

The goal of mapping is to provide callable key-value tables that can be manipulated as {vctrs}.

## Installation


``` r
install.packages("jameelalsalam/mapping")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(mapping)
suppressPackageStartupMessages(library(tidyverse))
## basic example code

countries <- c("FR", "GR", "IT")
capitals  <- c("Paris", "Berlin", "Rome")

eu_caps <- mapping(countries, capitals)

```

Display:
```{r display}
eu_caps
```


Apply the mapping:
```{r apply}
eu_caps(countries)
```

Use in tidyverse pipelines:
```{r tv}
tibble(
  countries = c("FR", "FR", "IT", "GR")
) %>%
  mutate(capitals = eu_caps(countries))
```


The keys, values, and keyvalues can be retrieved, queried, and modified:
```{r query}
mapping_keys(eu_caps)

mapping_values(eu_caps)
```



```{r modify}

```


In future, it will go inside a tibble:

```{r intbl}

  
```

```{r indf}
# data.frame(
#   kv = eu_caps
# )
```

Compose mappings:
```{r compose}

```


