---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mappers

<!-- badges: start -->
<!-- badges: end -->

The goal of mappers is to provide a {vctrs} compatible key-value type, coercible with rlang::as_mapper

## Installation

You can install the released version of mappers from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("mappers")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(tibble)
library(mappers)
## basic example code

countries <- c("FR", "GR", "IT")
capitals  <- c("pa", "be", "ro")

eu_caps <- keyvalue(countries, capitals)
eu_caps
```

Check status:
```{r}
is_keyvalue(eu_caps)
```


It can go inside a tibble: (although doesn't show up right in Rstudio notebook)

```{r cars}
tibble(
  kv = eu_caps
)
```

```{r}
data.frame(
  kv = eu_caps
)
```


You can also embed plots, for example:

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!
